\documentclass[a4paper,11pt]{article}

% Package imports
\usepackage{calligra}
\usepackage{mathrsfs}
\usepackage{latexsym}
\usepackage{ragged2e}
\usepackage{xcolor}
\usepackage{float}
\usepackage{ragged2e}
\usepackage[empty]{fullpage}
\usepackage{wrapfig}
\usepackage{lipsum}
\usepackage{tabularx}
\usepackage{titlesec}
\usepackage{geometry}
\usepackage{marvosym}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage{fancyhdr}
\usepackage{multicol}
\usepackage{graphicx}
\usepackage{cfr-lm}
\usepackage[T1]{fontenc}
\usepackage{fontawesome5}

% Color definitions
\definecolor{darkblue}{RGB}{0,0,139}

% Page layout
\setlength{\multicolsep}{0pt} 
\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\geometry{left=1.4cm, top=0.8cm, right=1.2cm, bottom=1cm}
\setlength{\footskip}{5pt} % Addressing fancyhdr warning

% Hyperlink setup (moved after fancyhdr to address warning)
\usepackage[hidelinks]{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=darkblue,
    filecolor=darkblue,
    urlcolor=darkblue,
}

% Custom box settings
\usepackage[most]{tcolorbox}
\tcbset{
    frame code={},
    center title,
    left=0pt,
    right=0pt,
    top=0pt,
    bottom=0pt,
    colback=gray!20,
    colframe=white,
    width=\dimexpr\textwidth\relax,
    enlarge left by=-2mm,
    boxsep=4pt,
    arc=0pt,outer arc=0pt,
}

% URL style
\urlstyle{same}

% Text alignment
\raggedright
\setlength{\tabcolsep}{0in}

% Section formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-7pt}]

% Custom commands
\newcommand{\resumeItem}[2]{
  \item{
    \textbf{#1}{\hspace{0.5mm}#2 \vspace{-0.5mm}}
  }
}

\newcommand{\resumePOR}[3]{
\vspace{0.5mm}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
        \textbf{#1}\hspace{0.3mm}#2 & \textit{\small{#3}} 
    \end{tabular*}
    \vspace{-2mm}
}

\newcommand{\resumeSubheading}[4]{
\vspace{0.5mm}\item
    \begin{tabular*}{0.98\textwidth}[t]{l@{\extracolsep{\fill}}r}
        \textbf{#1} & \textit{\footnotesize{#4}} \\
        \textit{\footnotesize{#3}} &  \footnotesize{#2}\\
    \end{tabular*}
    \vspace{-2.4mm}
}

\newcommand{\resumeProject}[4]{
\vspace{0.5mm}\item
    \begin{tabular*}{0.98\textwidth}[t]{l@{\extracolsep{\fill}}r}
        \textbf{#1} & \textit{\footnotesize{#3}} \\
        \footnotesize{\textit{#2}} & \footnotesize{#4}
    \end{tabular*}
    \vspace{-2.4mm}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemi}{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand{\labelitemii}{$\vcenter{\hbox{\tiny$\circ$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*,labelsep=1mm]}
\newcommand{\resumeHeadingSkillStart}{\begin{itemize}[leftmargin=*,itemsep=1.7mm, rightmargin=2ex]}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*,labelsep=1mm,itemsep=0.5mm]}

\newcommand{\resumeSubHeadingListEnd}{\end{itemize}\vspace{2mm}}
\newcommand{\resumeHeadingSkillEnd}{\end{itemize}\vspace{-2mm}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-2mm}}
\newcommand{\cvsection}[1]{%
\vspace{2mm}
\begin{tcolorbox}
    \textbf{\large #1}
\end{tcolorbox}
    \vspace{-4mm}
}

\newcolumntype{L}{>{\raggedright\arraybackslash}X}%
\newcolumntype{R}{>{\raggedleft\arraybackslash}X}%
\newcolumntype{C}{>{\centering\arraybackslash}X}%

% Commands for icon sizing and positioning
\newcommand{\socialicon}[1]{\raisebox{-0.05em}{\resizebox{!}{1em}{#1}}}
\newcommand{\ieeeicon}[1]{\raisebox{-0.3em}{\resizebox{!}{1.3em}{#1}}}

% Font options
\newcommand{\headerfonti}{\fontfamily{phv}\selectfont} % Helvetica-like (similar to Arial/Calibri)
\newcommand{\headerfontii}{\fontfamily{ptm}\selectfont} % Times-like (similar to Times New Roman)
\newcommand{\headerfontiii}{\fontfamily{ppl}\selectfont} % Palatino (elegant serif)
\newcommand{\headerfontiv}{\fontfamily{pbk}\selectfont} % Bookman (readable serif)
\newcommand{\headerfontv}{\fontfamily{pag}\selectfont} % Avant Garde-like (similar to Trebuchet MS)
\newcommand{\headerfontvi}{\fontfamily{cmss}\selectfont} % Computer Modern Sans Serif
\newcommand{\headerfontvii}{\fontfamily{qhv}\selectfont} % Quasi-Helvetica (another Arial/Calibri alternative)
\newcommand{\headerfontviii}{\fontfamily{qpl}\selectfont} % Quasi-Palatino (another elegant serif option)
\newcommand{\headerfontix}{\fontfamily{qtm}\selectfont} % Quasi-Times (another Times New Roman alternative)
\newcommand{\headerfontx}{\fontfamily{bch}\selectfont} % Charter (clean serif font)

\begin{document}
\begin{justify}
\headerfontiii

% Header
\begin{center}
    {\Huge\textbf{Guojia WU}}
\end{center}
\vspace{-2mm}

\begin{center}
    \small{
    (+86) 18058740766 | \href{https://wuguojia@tmu.edu.cn}{wuguojia@tmu.edu.cn} | 
    \href{https://github.com/wunaiwuhuang}{github.com/wunaiwuhuang}
    }
\end{center}
\vspace{-8mm}

% \begin{center}
%     \small{
%     \socialicon{\faGithub} \href{https://github.com/wunaiwuhuang}{https://github.com/wunaiwuhuang} | 
%     \socialicon{\faTwitter} \href{https://x.com/mcintyre_l4546}{mcintyre\_l4546}
%     }
% \end{center}
% \vspace{-7mm}
% \begin{center}
%     \small{TianJin Medical University(TMU), HePin, TianJin - 300070, China}
% \end{center}

\vspace{2mm}

\section{\large{\textbf{RESEARCH INTEREST}}}
\vspace{1mm}
{
With a strong foundation in both basic medicine and bioinformatics, I specialize in applying bioinformatics techniques to investigate cancer biology, particularly focusing on the roles of genomics and epigenetic modifications in tumor development and progression. I am also interested in tumor immune infiltration and its interaction with the genomic and epigenetic landscape. I am passionate about identifying potential therapeutic targets through integrative bioinformatics analyses, and exploring how genetic and methylation alterations contribute to cancer development and treatment response.
}
\vspace{-2mm}



% \section{\textbf{Experience}}
% \vspace{-0.4mm}
%   \resumeSubHeadingListStart
%   \resumeSubheading
%       {{Company A [\href{https://www.companya.com}{\faIcon{globe}}]}}{City, Country}
%       {Job Title A}{Month Year - Month Year}
%       \resumeItemListStart
%         \item Developed [specific achievement] achieving [specific metric] in [specific area]
%         \item Implemented [technology/method], enhancing [specific aspect] by [specific percentage]
%         \item Conducted analysis on [specific data], identifying [key findings]
%         \item Presented findings at [specific event], receiving [specific recognition]
%       \resumeItemListEnd 
%   \resumeSubheading
%     {Company B [\href{https://www.companyb.com}{\faIcon{globe}}]}{Remote}
%     {Job Title B}{Month Year - Month Year}
%     \resumeItemListStart
%       \item Engineered a [specific system/model], improving [specific metric] by [percentage]
%       \item Developed [specific tool/method], increasing [specific aspect] by [percentage]
%       \item Implemented [specific system], reducing [specific metric] by [percentage]
%       \item Conducted [specific test/analysis] to validate [specific aspect]
%     \resumeItemListEnd
%   \resumeSubHeadingListEnd
% \vspace{-6mm}

\vspace{1mm}
\section{
  \large{\textbf{EDUCATION}} \hfill 
  \href{https://github.com/wunaiwuhuang/materials}{\textcolor{darkblue}{\faGithub}}
  }
\vspace{-0.4mm}
\resumeSubHeadingListStart

\resumeSubheading
{TianJin Medical University}{TianJin, China}
{Bachelor of Science in \textbf{Basic Medicine}}{Sep. 2021 - Jun. 2026  (Expected)}
\resumeItemListStart
\item \textbf{GPA:} 3.77/4.00; \ \ \ \ \ \textbf{RANKING :} 1st out of 22 students;\ \ \ \ \ \  \textbf{IELTs:} 7.0, C 1;
\resumeItemListEnd

% \resumeSubheading
% {College Name}{City, Country}
% {Pre-University Education}{Month Year}
% \resumeItemListStart
% \item Grade: XX.X\%
% \resumeItemListEnd

% \resumeSubheading
% {High School Name}{City, Country}
% {Secondary Education}{Month Year}
% \resumeItemListStart
% \item GPA: X.X/10
% \resumeItemListEnd

\resumeSubHeadingListEnd
\vspace{-8mm}

\section{\large{\textbf{RESEARCH PROJECTS}}}
\vspace{-0.6mm}
\resumeSubHeadingListStart
\resumeProject
  {Pan-Cancer Atlas of TCGA ipaQTM \small{(Independent project)}}
  {Supervisor: \textbf{Prof. Yang Yang} \ \ \ Supported by YY Lab, TMU;}
  {Mar. 2025 - Present}
  {{}[\href{https://github.com/wunaiwuhuang/materials/tree/main/Award\_and\_honour\%E8\%8E\%B7\%E5\%A5\%96\%E8\%AF\%81\%E6\%98\%8E/innovation\%20and\%20Entrepreneurship\%20Competition}{\textcolor{darkblue}{\faGithub}}]}
\resumeItemListStart
  \item \textbf{Investigated the relationship between DNA methylation and intronic pre-mRNA polyadenylation (IPA) across 23 cancer types using TCGA data, and further explored the underlying mechanisms}, including trans effects from genes such as \textit{CDK12, BCL2, and CPSF1}, as well as cis effects involving DNA structure and transcription factor binding (e.g., \textit{CTCF}). These findings suggested a novel regulatory layer in cancer transcriptomics.
  \item Constructed a pan-cancer ipaQTM (intron polyadenylation quantitative trait methylation) map using Inpact and MatrixEQTL, \textbf{identifying over 500,000 cis-/trans- associations, Discovered thousands of putative IPA regulators.} 
\resumeItemListEnd

\resumeProject
  {Glycolysis-Related Subtypes in Hepatocellular Carcinoma \small{(Independent project)}}
  {Supervisor: \textbf{Prof. Yongmei Li} \ \ \ Supported by TMU Yongmei Li Lab;}
  {Mar. 2025 - Present}
  {{}[\href{https://github.com/wunaiwuhuang/materials/tree/main/Award\_and\_honour\%E8\%8E\%B7\%E5\%A5\%96\%E8\%AF\%81\%E6\%98\%8E/innovation\%20and\%20Entrepreneurship\%20Competition}{\textcolor{darkblue}{\faGithub}}]}
\resumeItemListStart
  \item Identified key glycolysis-related genes (e.g., \textit{SMG1}, \textit{SRRM2}, \textit{STAG1}) associated with hepatocellular carcinoma (HCC) progression through integrative analysis of RNA-seq, somatic mutation, and DNA methylation data. \textbf{Constructed a glycolytic gene signature using PCA and CatBoost-based feature selection from 30 candidate genes, and developed a molecular subtyping model based on non-negative matrix factorization (NMF).} This model stratified patients into clinically distinct subtypes with significant differences in survival, tumor stage, and metabolic activity, thereby demonstrating potential diagnostic and prognostic utility. 
  \item Glycolysis levels inferred from RNA-seq were correlated with immune infiltration patterns by integrating ESTIMATE and CIBERSORT algorithms, revealing subtype-specific immune microenvironments relevant to immunotherapy response.
\resumeItemListEnd

\resumeProject
  {Comprehensive Benchmark of DNN-Based pMHC Predictors \small{(Independent project)}}
  {Supervisor: \textbf{Prof. Yang Yang} \ \ \ Supported by TMU YY Lab;}
  {Sep. 2024 - Jan. 2025}
  {{}[\href{https://github.com/wunaiwuhuang/materials/tree/main/Award\_and\_honour\%E8\%8E\%B7\%E5\%A5\%96\%E8\%AF\%81\%E6\%98\%8E/innovation\%20and\%20Entrepreneurship\%20Competition}{\textcolor{darkblue}{\faGithub}}]}
\resumeItemListStart
  \item Benchmarked 17 state-of-the-art DNN-based tools for HLA-I peptide binding prediction using a \textbf{self-curated dataset of 290,000+ peptides across 44 alleles. Assessed model accuracy, robustness, and interpretability; incorporated SHAP and LIME to reveal internal mechanisms and feature contributions}.
  \item Found self-attention models (STMHCpan, BigMHC) achieved best overall performance, while capsule-based CapsNet-MHC\_AN showed strong generalizability. Demonstrated that models trained on eluted ligand data outperform those using binding affinity data; ensemble strategies further improved reliability.
  \item Provided actionable guidelines for model selection, data integration, and the design of interpretable, clinically useful immunoinformatics tools.
\resumeItemListEnd

\resumeProject
  {The role of HADH Isoform 3 in Endometrial Cancer \small{(Independent project)}}
  {Supervisor: \textbf{Prof. Yongmei Li} \ \ \ Supported by TMUUROP Fund (1,000 RMB);}
  {Mar. 2023 - Aug. 2024}
  {{}[\href{https://github.com/wunaiwuhuang/materials/tree/main/Award\_and\_honour\%E8\%8E\%B7\%E5\%A5\%96\%E8\%AF\%81\%E6\%98\%8E/innovation\%20and\%20Entrepreneurship\%20Competition}{\textcolor{darkblue}{\faGithub}}]}
\resumeItemListStart
  \item \textbf{Identified the link between the fatty acid metabolism gene \textit{HADH} and endometrial cancer (EC) using RNA-seq, genomics, and metabolomics data analysis.} Discovered \textit{HADH} isoform 3 is downregulated in EC through \textit{DDX3X} suppression, leading to activation of the \textit{MEK-ERK} signaling pathway and promotion of malignant EC phenotypes.
  \item Demonstrated the therapeutic potential of \textit{HADH} as a biomarker for EC, and its role in tumor infiltration and microenvironment construction.
  \item Provided insights for improved EC diagnosis, treatment, and prognosis monitoring by mapping the complete pathway of \textit{HADH-DDX3X-MEK/ERK} interaction.
\resumeItemListEnd

\resumeProject
  {The role of Raptor in Post-Ischemic Angiogenesis \small{(Collaborative project)}}
  {Supervisor: \textbf{Prof. Ding Ai} \ \ \ Supported by TMUUROP Fund (20,000 RMB);}
  {Apr. 2022 - Aug. 2023}
  {{}[\href{https://github.com/wunaiwuhuang/materials/tree/main/Award\_and\_honour\%E8\%8E\%B7\%E5\%A5\%96\%E8\%AF\%81\%E6\%98\%8E/innovation\%20and\%20Entrepreneurship\%20Competition}{\textcolor{darkblue}{\faGithub}}]}
\resumeItemListStart
  \item \textbf{Investigated the role of Raptor, a core component of the mTORC1 complex, in post-ischemic angiogenesis using both in vivo and in vitro models.}
  \item Explored the contribution of mTORC1 signaling in vascular regeneration, providing novel insights into the molecular regulation of ischemia-induced angiogenesis. Potentially offering new therapeutic strategies for peripheral artery disease by targeting the Raptor/mTORC1 pathway to enhance revascularization and tissue recovery.
\resumeItemListEnd

\resumeProject
  {The role of Annexin A2 in Hepatocarcinogenesis \small{(Collaborative project)}}
  {Supervisor: \textbf{Prof. Chunjiong Wang} \ \ \ Supported by TMUUROP Fund (10,000 RMB);}
  {Apr. 2022 - Aug. 2023}
  {{}[\href{https://github.com/wunaiwuhuang/materials/tree/main/Award\_and\_honour\%E8\%8E\%B7\%E5\%A5\%96\%E8\%AF\%81\%E6\%98\%8E/innovation\%20and\%20Entrepreneurship\%20Competition}{\textcolor{darkblue}{\faGithub}}]}
\resumeItemListStart
  \item Investigated the differential roles of \textit{ANXA2} in normal liver regeneration and hepatocellular carcinoma (HCC) development. Identified \textit{ANXA2} upregulates cholesterol biosynthesis, enhancing hepatocyte proliferation via increased intracellular cholesterol.
  \item \textbf{Combined transcriptomic and metabolomic approaches to explore how \textit{ANXA2}-mediated cholesterol regulation contributes to HCC progression.} Found \textit{ANXA2} as a potential dual-function target to simultaneously suppress HCC and promote normal liver regeneration after partial hepatectomy.
\resumeItemListEnd
\resumeSubHeadingListEnd

\section{
  \large{\textbf{PUBLICATIONS}} \hfill 
  \textcolor{darkblue}{\scriptsize A=Research article, R=Review, P=Publication, S=In Submission}
  {\scriptsize\hspace{0.5em}[\href{https://github.com/wunaiwuhuang/materials/tree/main/My\_articles\%E8\%AE\%BA\%E6\%96\%87\%E8\%AF\%81\%E6\%98\%8E}{\textcolor{darkblue}{\faGithub}}]}
}
\small{
\begin{enumerate}[leftmargin=*, labelsep=0.5em, align=left, widest={[\textbf{S.1}]}, itemindent=0em, label={\textbf{[\arabic*]}]}]

\item[\textbf{[AS.1]}] \textbf{Wu, G.}, Liu, X., Wang, Y., \& Yang, Y. (2025). \textbf{omprehensive evaluation and interpretative insights of peptide-HLA binding prediction tools using explainable artificial intelligence.} \textit{bioRxiv.}

\item[\textbf{[AP.1]}]  \textbf{Sun, L., Zhai, S., Wu, G.}, Gu, J., Huang, Y., Hong, D., Wang, J., \& Li, Y. (2024). \textbf{Diagnostic sensitivity of immune-inflammatory cell proportion in early diagnosis of endometrial cancer}. \textit{Clinical Surgical Oncology.}

\item[\textbf{[AS.2]}] \textbf{Li, W., Guo, R., Zhang, R.}, Wu, G., Chen, R., \& Wang, D. (2025). \textbf{A bibliometric analysis of immunotherapy in glioblastoma}. Manuscript under review.

\item[\textbf{[RP.1]}] \textbf{Wu, G.}, Zhai, S., Sun, X., Huang, Y., Li, Y., \& Sun, L. (2024). \textbf{progress of the effect of hydroxyacyl-coenzyme A dehydrogenase in cancer development and its mechanism}. \textit{Basic \& Clinical Medicine}.
% \item[\textbf{[J.1]}] Author 1, Your Name, Author 3, et al. (Year). \href{https://doi.org/XX.XXXX/XXXXX.XXXX.XXXXXXX}{\textbf{Title of Journal Article}}. \textit{Journal Name}, Vol. XX, Issue X, pp. XXX-XXX. DOI: XX.XXXX/XXXXX.XXXX.XXXXXXX
\end{enumerate}
}

\section{\large{\textbf{ACADEMIC SKILLS}}}
\vspace{-0.4mm}
 \resumeHeadingSkillStart
  \resumeSubItem{Programming Languages:}
    {\textbf{R, Python, html and Shell.}}
  \resumeSubItem{Wet Lab Techniques:}
    {Western blotting, DNA electrophoresis, plasmid construction and extraction, PCR, cell culture, migration and invasion assays, CCK-8 assay, tumor formation in mice, immunohistochemistry, etc.}
  \resumeSubItem{Bioinformatics Skills:}
    {RNA-seq analysis, database construction, sequence alignment, methylation and mutation analysis, CNV detection, gene enrichment and survival analysis, tumor subtyping, PPI network analysis, immune cell infiltration, Seurat-based single-cell analysis, QTL mapping, XAI teniques(SHAP,LIME) etc.}
  % \resumeSubItem{Web Technologies:}
  %   {Technology 1, Technology 2, Technology 3, Technology 4, Technology 5}
  % \resumeSubItem{Database Systems:}
  %   {Database 1, Database 2, Database 3}
  % \resumeSubItem{Data Science \& Machine Learning:}
  %   {Tool 1, Tool 2, Tool 3, Tool 4, Tool 5, Tool 6}
  \resumeSubItem{Research Skills:}
    {Operating system proficiency (\textbf{Windows, CentOS, Mint, Ubuntu}); Presentation (\textbf{LaTeX, PowerPoint, Photoshop, Adobe Illustrator}); Academic writing; Data processing; Reference management, etc.}
 \resumeHeadingSkillEnd

\section{\large{\textbf{HONOUR AND SCHOLARSHIP}}}
\vspace{-0.4mm}
\resumeSubHeadingListStart

\resumeProject
  {TianJin Medical University Scholarship -- Merit Student}
  {TianJin Medical University}
  {2021 - 2022}
  {{}[\href{https://github.com/wunaiwuhuang/materials/tree/main/Award\_and\_honour\%E8\%8E\%B7\%E5\%A5\%96\%E8\%AF\%81\%E6\%98\%8E/scholarship}{\textcolor{darkblue}{\faIcon{globe}}}]}
\resumeItemListStart
  \item Ranked in top 1\% of students in TianJin Medical University.
\resumeItemListEnd

\resumeProject
  {TianJin Medical University Scholarship -- First Prize}
  {TianJin Medical University}
  {2022 - 2023}
  {{}[\href{https://github.com/wunaiwuhuang/materials/tree/main/Award\_and\_honour\%E8\%8E\%B7\%E5\%A5\%96\%E8\%AF\%81\%E6\%98\%8E/scholarship}{\textcolor{darkblue}{\faIcon{globe}}}]}
\resumeItemListStart
  \item Ranked in top 5\% of students in TianJin Medical University.
\resumeItemListEnd

\resumeProject
  {TianJin Medical University Scholarship -- First Prize}
  {TianJin Medical University}
  {2023 - 2024}
  {{}[\href{https://github.com/wunaiwuhuang/materials/tree/main/Award\_and\_honour\%E8\%8E\%B7\%E5\%A5\%96\%E8\%AF\%81\%E6\%98\%8E/scholarship}{\textcolor{darkblue}{\faIcon{globe}}}]}
\resumeItemListStart
  \item Ranked in top 5\% of students in TianJin Medical University.
\resumeItemListEnd

\resumeSubHeadingListEnd

\vspace{-6mm}
\section{\large{\textbf{EXPERIENCES AND AWARDS}}}
\vspace{-0.4mm}
\resumeSubHeadingListStart
\resumeProject
{Teaching Assistant in Pathogenic Organisms}
{TianJin Medical University, College of Basic Medicine in association with \textbf{Prof. Yongmei Li}}
{Apr. 2023- Jun. 2023}
{}
{}
\resumeProject
  {Executive Member, Basic Medicine Student Association}
  {College of Basic Medicine, TianJin Medical University}
  {Sep. 2021 - Jun. 2025}
  {{}[\href{https://github.com/wunaiwuhuang/materials/tree/main/Award\_and\_honour\%E8\%8E\%B7\%E5\%A5\%96\%E8\%AF\%81\%E6\%98\%8E/volunteering\%20awards}{\textcolor{darkblue}{\faIcon{globe}}}]}
\resumeItemListStart
  \item Executed a wide range of volunteer programs within the College of Life Sciences, including social practice, community outreach, and campus-wide events such as the university sports meeting and services for the visually impaired.
  \item Led the recruitment and training of new volunteers, and designed engaging volunteer initiatives to enhance student union participation in public service.
\resumeItemListEnd
\resumeProject
  {Third Prize, International Forum on Basic Medical Sciences}
  {National Demonstration Center for Experimental Education}
  {Aug. 2024}
  {{}[\href{https://github.com/wunaiwuhuang/materials/tree/main/Award\_and\_honour\%E8\%8E\%B7\%E5\%A5\%96\%E8\%AF\%81\%E6\%98\%8E/innovation\%20and\%20Entrepreneurship\%20Competition}{\textcolor{darkblue}{\faIcon{globe}}}]}
\resumeItemListStart
  \item Led Tianjin Medical University's first participation in the “Belt and Road” International Track; responsible for experimental design, and delivered the entire presentation and defense in English as team leader.
\resumeItemListEnd
\resumeProject
  {Third Prize in the Chinese Mathematics Competitions}
  {Chinese Mathematical Society}
  {Dec. 2023}
  {{}[\href{https://github.com/wunaiwuhuang/materials/tree/main/Award\_and\_honour\%E8\%8E\%B7\%E5\%A5\%96\%E8\%AF\%81\%E6\%98\%8E/academic\%20compeletion}{\textcolor{darkblue}{\faIcon{globe}}}]}
\resumeProject
  {Third prize, TianJin Chemistry competition}
  {Tianjin Municipal Education Commission}
  {Oct. 2023}
  {{}[\href{https://github.com/wunaiwuhuang/materials/tree/main/Award\_and\_honour\%E8\%8E\%B7\%E5\%A5\%96\%E8\%AF\%81\%E6\%98\%8E/academic\%20compeletion}{\textcolor{darkblue}{\faIcon{globe}}}]}
\resumeProject
  {Third prize, TianJin biology experimental competition}
  {Tianjin Municipal Education Commission}
  {Oct. 2024}
  {{}[\href{https://jwc.nankai.edu.cn/2024/1028/c35436a553965/page.htm}{\textcolor{darkblue}{\faIcon{globe}}}]}
\resumeProject
  {First Prize (best), Internet Innovation and Entrepreneurship Competition}
  {Ministy of Education of the People's Repubulic of China}
  {2022 - 2024}
  {{}[\href{https://github.com/wunaiwuhuang/materials/tree/main/Award\_and\_honour\%E8\%8E\%B7\%E5\%A5\%96\%E8\%AF\%81\%E6\%98\%8E/innovation\%20and\%20Entrepreneurship\%20Competition}{\textcolor{darkblue}{\faIcon{globe}}}]}
  \resumeItemListStart
  \item Participated in the entrepreneurship track of the Internet Innovation and Entrepreneurship Competition for three consecutive years, serving as project leader or core member. Got over 8 awards in this competitions.
  \resumeItemListEnd
\resumeProject
  {Second Prize (best),  Challenge Cup National undergraduate entrepreneurship plan competition}
  {Ministy of Education of the People's Repubulic of China}
  {2023 - 2024}
  {{}[\href{https://github.com/wunaiwuhuang/materials/tree/main/Award\_and\_honour\%E8\%8E\%B7\%E5\%A5\%96\%E8\%AF\%81\%E6\%98\%8E/innovation\%20and\%20Entrepreneurship\%20Competition}{\textcolor{darkblue}{\faIcon{globe}}}]}
  \resumeItemListStart
  \item Participated in the Challenge Cup innovation track for two consecutive years as project leader, successfully leading the proposal submission and project execution each year. Got over 3 awards in this competitions.
  \resumeItemListEnd
\resumeProject
  {Second Prize (best),  Tianjin medical university TMUSPIP}
  {TianJin Medical University}
  {2023 - 2024}
  {{}[\href{https://github.com/wunaiwuhuang/materials/tree/main/Award\_and\_honour\%E8\%8E\%B7\%E5\%A5\%96\%E8\%AF\%81\%E6\%98\%8E/volunteering\%20awards}{\textcolor{darkblue}{\faIcon{globe}}}]}
  \resumeItemListStart
  \item Participated in TMUSPIP, Tianjin Medical University's social practice initiative, for three consecutive years as a project leader or core team member; each year successfully secured university-level funding and completed the project with approved final reports; Got over 3 awards in TMUSPIP.
  \resumeItemListEnd
\resumeSubHeadingListEnd

\vspace{-6mm}

% \section{\textbf{Volunteer Experience}}
% \vspace{-0.4mm}
% \resumeSubHeadingListStart
% \resumeProject
%   {Volunteer Role A}
%   {Organization Name}
%   {Month Year - Month Year}
%   {{}[\href{https://volunteer-org-a-link.com}{\textcolor{darkblue}{\faIcon{globe}}}]}
% \resumeItemListStart
%   \item Key responsibility or contribution in this role
%   \item Impact of your volunteer work
%   \item Skills developed or applied during this experience
% \resumeItemListEnd

% \resumeProject
%   {Volunteer Role B}
%   {Organization Name}
%   {Month Year - Present}
%   {{}[\href{https://volunteer-org-b-link.com}{\textcolor{darkblue}{\faIcon{globe}}}]}
% \resumeItemListStart
%   \item Key responsibility or contribution in this role
%   \item Impact of your volunteer work
%   \item Skills developed or applied during this experience
% \resumeItemListEnd

% \resumeSubHeadingListEnd
% \vspace{-6mm}

% \section{\textbf{Professional Memberships}}
% \vspace{-0.4mm}
% \resumeSubHeadingListStart
% \resumePOR{Professional Organization A}
%     {, Membership ID: XXXXXXXX}
%     {Month Year - Present}
% \resumePOR{Professional Organization B}
%     {, \href{https://membership-certificate-link.com}{Membership ID: XXXXXXXX}}
%     {Month Year - Present}
% \resumePOR{Professional Organization C}
%     {, \href{https://membership-certificate-link.com}{Membership ID: XXXXXXXX}}
%     {Month Year - Present}

% \resumeSubHeadingListEnd
% \vspace{-6mm}

% \section{\textbf{Certifications}}
% \vspace{-0.2mm}
% \resumeSubHeadingListStart
% \resumePOR{}{\href{https://certification-link-a.com}{
% \textbf{Certification A}
% }}{Month Year}
% \resumePOR{}{
% \textbf{Certifying Body:} {{\href{https://certification-link-b.com}{Certification B}}}}{Month Year}
% \resumePOR{}{
% \textbf{Certifying Body:} {{\href{https://certification-link-c.com}{Certification C}}}}{Month Year}
% \resumePOR{}{\href{https://certification-link-d.com}{
% \textbf{Certification D}
% }}{Month Year}

% \resumeSubHeadingListEnd
% \vspace{-6mm}

% \section{\textbf{Additional Information}}
% \vspace{-0.4mm}
% \small{
% \textbf{Languages:} Language A (Proficiency level), Language B (Proficiency level), Language C (Proficiency level)

% \textbf{Interests:} Interest 1, Interest 2, Interest 3, Interest 4
% }
% \vspace{-4mm}


% \section{\textbf{References}}
% \vspace{-0.2mm}
% \small{
% \begin{enumerate}[leftmargin=*,labelsep=2mm]
% \item \textbf{Reference Person 1}\\
%    Job Title, Department\\
%    Organization/Institution Name\\
%    Email: email1@example.com\\
%    Phone: +X-XXX-XXX-XXXX\\
%    \textit{Relationship: [e.g., Thesis Advisor, Manager, etc.]}

% \item \textbf{Reference Person 2}\\
%    Job Title, Department\\
%    Organization/Institution Name\\
%    Email: email2@example.com\\
%    Phone: +X-XXX-XXX-XXXX\\
%    \textit{Relationship: [e.g., Project Supervisor, Colleague, etc.]}

% \item \textbf{Reference Person 3}\\
%    Job Title, Department\\
%    Organization/Institution Name\\
%    Email: email3@example.com\\
%    Phone: +X-XXX-XXX-XXXX\\
%    \textit{Relationship: [e.g., Mentor, Collaborator, etc.]}
% \end{enumerate}
% }
\end{justify}
\end{document}